---
title: "Vacant City-Owned Properties in Central Brooklyn"
author: "Danylo Orlov"
date: "`r format(Sys.Date())`"
output:
  word_document:
    toc: yes
    toc_depth: '2'
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First, let's load all necessary packages:

```{r}
library(knitr)
library(dplyr)
library(flextable)
```

Let us first load the file:

```{r, warning=F}
COLP=read.csv("~/Documents/vacanthome/data/input/COLP.csv")
```

We can restirct the dataset to only include city-owned Brooklyn properties with no current use:

```{r}
data_brooklyn <- COLP %>%
  filter(BOROUGH == 3 & OWNERSHIP == "C" & CATEGORY == 3)
```

Now, let's see how many vacant properties there are in Brooklyn:

```{r}
data_brooklyn_s <- data_brooklyn %>%
  group_by(USE.TYPE) %>%
  summarize(number = n())
print(data_brooklyn_s)
```

There are 549 vacant land areas in Brooklyn, and 13 non-residential structures without any use. 

Let's now zoom in on Central Brooklyn, which I am defining to include the following community districts: 302, 303, 306, 308, 309

```{r}
data_central_brooklyn <- data_brooklyn %>%
  filter(CD %in% c(302, 303, 306, 308, 309))
```

Let's save this data that includes just those five community districts:

```{r}
save(data_central_brooklyn, file = "data_central_brooklyn.RData")
```

We can now summarize the data again:

```{r}
data_central_brooklyn_s <- data_central_brooklyn %>%
  group_by(USE.TYPE) %>%
  summarize(number = n())
print(data_central_brooklyn_s)
```

There are 170 vacant land areas in Central Brooklyn, and 5 non-residential structures without any use. 

Let's now list all five non-residential structures in Central Brooklyn without any use in a nice table:

```{r}
#filter and rename columns
filtered_data_buildings <- data_central_brooklyn %>%
  filter(USE.TYPE == "NO USE-NON RESIDENTIAL STRUCTURE") %>%
  select(
    `Community District` = CD, 
    `House Number` = HOUSE.NUMBER, 
    `Street Name` = STREET.NAME, 
    `Address` = ADDRESS, 
    `Parcel Name` = PARCEL.NAME, 
    `Agency` = AGENCY
  )

#create a formatted table
table_buildings <- flextable(filtered_data_buildings) %>%
  set_caption("List of Non-Residential Structures in Central Brooklyn") %>%
  autofit() %>%
  width(j = 1:6, width = c(1, 1, 1.5, 2, 2, 1))

#print the formatted table
table_buildings
```

And now let's do the same for all 170 vacant land areas:

```{r}
#filter and rename columns
filtered_data_land <- data_central_brooklyn %>%
  filter(USE.TYPE == "NO USE-VACANT LAND") %>%
  select(
    `Community District` = CD, 
    `House Number` = HOUSE.NUMBER, 
    `Street Name` = STREET.NAME, 
    `Address` = ADDRESS, 
    `Parcel Name` = PARCEL.NAME, 
    `Agency` = AGENCY
  )

#create a formatted table
table_land <- flextable(filtered_data_land) %>%
  set_caption("List of Vacant Land Areas in Central Brooklyn") %>%
  autofit() %>%
  width(j = 1:6, width = c(1, 1, 1.5, 2, 2, 1))

#print the formatted table
table_land
```






